### 2024-08-08 Article/main.tex
Introduction to graphs with equivalence and readme

A first obvious definition of graph is given via sets and set-theoretic tools. The next definition recalls how a graph intuitively is.

>>>>

First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.

\subsection{Simple Graphs}
